---
title: "Cardamom Roll Ingredients"
teaching: 10
exercises: 2
---

:::::::::::::::::::::::::::::::::::::: questions 

- What are the ingredients needed for the cardamom rolls?

::::::::::::::::::::::::::::::::::::::::::::::::

::::::::::::::::::::::::::::::::::::: objectives

- Be able to put together your shopping list
- Convert between metric and imperial units, if necessary
- Double the recipe if you're really hungry

::::::::::::::::::::::::::::::::::::::::::::::::

```{r setup, include=FALSE}
library(tidyverse)
```


## Ingredients

There are 3 main components to this recipe: the main ingredients for the dough, the ingredients for the cardamom-sugar filling, and the ingredients for the glaze.

### Dough Ingredients

```{r ingredients}
main_ingredients <- tribble(
  ~ingredient, ~amount_imperial, ~amount_grams,
  "butter (cold)", "8 tablespoons", 113,
  "all-purpose flour", "2 ½ cups", 300,
  "sourdough starter discard", "⅓ cup", 100,
  "buttermilk", "1 cup", 240,
  "honey or granulated sugar", "1 tbsp + 1 tsp", 25,
  "fine sea salt", "¾ teaspoon", 4,
  "baking powder", "1 tsp", NA,
  "baking soda", "½ cup", NA)

main_ingredients %>% 
  kableExtra::kable(align = "r")
```

::::::::::::::::::::::::::::: callout

**Recipe modifications:**

You can use **active** sourdough starter instead of discard, if you so choose. There will be a slight modification to the recipe if that is the case.

In warmer climates, you may want to reduce the amount of buttermilk and/or increase the amount of flour to produce a less sticky, more manageable dough. You may have to experiment a bit.

:::::::::::::::::::::::::::::

### Cardamom-sugar filling

```{r}
filling_ingredients <- tribble(
  ~ingredient, ~amount_imperial, ~amount_grams,
  "light brown sugar", "¾ cup", 150,
  "ground cardamom", "2 teaspoons", NA,
  "butter (melted)", "4 tablespoons", 56)

filling_ingredients %>% 
  kableExtra::kable(align = "r")
```


### Glaze 

```{r}
glaze_ingredients <- tribble(
  ~ingredient, ~amount_imperial, ~amount_grams,
  "powdered sugar", "1 cup", 120,
  "butter (melted)", "1 tablespoon", 14,
  "vanilla extract", "1 teaspoon", 5,
  "milk", "2 tablespoons", 30)

glaze_ingredients %>% 
  kableExtra::kable(align = "r")
```

::::::::::::::::::::::::::::::::::::: instructor

It's worth emphasizing to your learners that there are many valid ways of accomplishing this task in R, whether using a `tidyverse` or base R approach.

::::::::::::::::::::::::::::::::::::: 


::::::::::::::::::::::::::::::::::::: challenge

Add a column to `main_ingredients` that has the amount in ounces (weight, not fluid oz).

::::::::::::::::::::::::::::::::::::: solution

```{r}
main_ingredients <- main_ingredients %>% 
  mutate(amount_oz = amount_grams * 0.035274)

main_ingredients
```


::::::::::::::::::::::::::::::::::::::::::::::::

::::::::::::::::::::::::::::::::::::::::::::::::
